R for Clinical Study Reports and Submission

### 2021-11-03 tlf-baseline.Rmd
Minor typo fix

For simplicity, we only analyze `SEX`, `AGE` and, `RACE` in this example
using the `table1` R package. More details of the `table` R package can
be found in the package
[vignettes](https://benjaminrich.github.io/table1/vignettes/table1-examples.html).

@@

The code below transfer the output into a dataframe
that only contain ASCII character
recommended by regulatory agencies.
`tbl_base` is used as input for `r2rtf` to create final report.

>>>>

For simplicity, we only analyze `SEX`, `AGE` and, `RACE` in this example
using the `table1` R package. More details of the `table1` R package can
be found in the package
[vignettes](https://benjaminrich.github.io/table1/vignettes/table1-examples.html).

@@

The code below transfer the output into a dataframe
that only contains ASCII characters
recommended by regulatory agencies.
`tbl_base` is used as input for `r2rtf` to create the final report.
